\documentclass[a4paper]{article}
\input{header}

\title{Entrepreneurial Risk}
\author{Summary \\ \\ Balázs Szekér \\ szekerb@student.ethz.ch \\ \\
    Summary of the Lecture Entrepreneurial Risk \\
    in the Spring Semester 2021 given by Didier Sornette \\ \\
    Swiss Federal Institute of Technology, ETH Zürich}

\renewcommand{\abstractname}{Preface}
\fancypagestyle{myplain}
{
  \fancyhf{}
  \renewcommand\headrulewidth{0pt}
  \renewcommand\footrulewidth{0pt}
  \fancyfoot[C]{\thepage}
}

\theoremstyle{definition}

\newtheorem*{theorem}{Theorem}
\newtheorem*{definition}{Definition}
\newtheorem*{lemma}{Lemma}
\newtheorem*{proposition}{Proposition}
\newtheorem*{example}{Example}
\newtheorem*{corollary}{Corollary}

\begin{document}    

\begin{titlepage}
    \maketitle
    \thispagestyle{empty}
\end{titlepage}

\newpage
\pagenumbering{Roman}
\thispagestyle{myplain}
\begin{abstract}
    This is a summary of the topics dealt with in the lecture Entrepreneurial
    Risk in the spring semester 2021 given by Didier Sornette at ETH Zürich.
    This script is based on the lecture slides provided by Prof. Didier Sornette.
    All images and illustrations in this Script were taken from the lecture
    slides. The list of topics is not exhaustive. Many things were left out and
    only the topics which the author regarded as important are mentioned.
    This summary should neither be considered as a replacement of the lecture nor as
    a sufficient preparation for the exam. This summary should only be a reminder to
    which you can resort in case you quickly want to look something up.
    No liability is accepted in the event of failure to pass the examination.

    \vspace{1\baselineskip}

    If you stumble over mistakes, be it linguistic or thematic, or if you have suggestions
    what to add or how to improve this script, do not hesitate to contact me at
    szekerb@student.ethz.ch.

    \vspace{1\baselineskip}

    Many Thanks
    
    \vspace{1\baselineskip}

    Balázs Szekér
\end{abstract}

\newpage
\thispagestyle{myplain}
\tableofcontents

\newpage

\pagenumbering{arabic}

\section{Introduction}

\input{Lectures/1_1_Entrepreneurship.tex}

\input{Lectures/1_2_Risks.tex}

\pagebreak

\input{Lectures/2_Setting_the_landscape_on_entrepreneurship_and_private_investment.tex}

\pagebreak

\input{Lectures/3_Introduction_to_company_valuation.tex}

\pagebreak

\input{Lectures/4_Wrapping_up_the_deal.tex}

\pagebreak

\input{Lectures/5_Logistic_equation_of_growth.tex}

\pagebreak

\input{Lectures/6_A_150_years_perspective.tex}

\pagebreak

\input{Lectures/7_China.tex}

\pagebreak

\input{Lectures/8_China_and_Switzerland.tex}

\pagebreak

\input{Lectures/9_Knowledge_and_economic_growth.tex}

\pagebreak

\input{Lectures/10_Humanity_in_the_Anthropocene.tex}

\end{document}