\documentclass[a4paper]{article}
\input{header}

\title{Complex Analysis}
\author{Summary \\ \\ Balázs Szekér \\ \href{mailto:szekerb@student.ethz.ch}{szekerb@student.ethz.ch} \\ \\
Summary of the Lecture Complex Analysis \\ in the Autumn Semester 2020 given by
Afonso Bandeira \\ \\ Swiss Federal Institute of Technology, ETH Zürich} 

\renewcommand{\abstractname}{Preface}

\begin{document}
\begin{titlepage}
    \maketitle
    \thispagestyle{empty}
\end{titlepage}
\pagebreak
\pagenumbering{Roman} 
\thispagestyle{myplain}
\begin{abstract}
    This is a summary of the topics dealt with in the lecture \textit{Complex
    Analysis} in the autumn semester 2020 given by Afonso Bandeira at ETH Zürich.
    This script is based on the lecture notes and the book \textit{Complex Analysis}
    by Lars Ahlfors.\footnote{[Ahlfors] - L. Ahlfors: "Complex analysis. An
    introduction to the theory of analytic functions of one complex variable."
    International Series in Pure and Applied Mathematics. McGraw-Hill Book Co.
    Link to an online PDF: \url{http://people.math.gatech.edu/~mccuan/courses/6321/lars-ahlfors-complex-analysis-third-edition-mcgraw-hill-science_engineering_math-1979.pdf}}
    The list of topics is not exhaustive. Many things were left out and only the
    topics which the author regarded as important are mentioned.
    This summary should neither be considered as a replacement of the lecture nor as
    a sufficient preparation for the exam. This summary should only be a reminder to
    which you can resort in case you quickly want to look something up.
    No liability is accepted in the event of failure to pass the examination.

    \vspace{1\baselineskip}

    If you stumble over mistakes, be it linguistic or thematic, or if you have suggestions
    what to add or how to improve this script, do not hesitate to contact me at
    \href{mailto:szekerb@student.ethz.ch}{szekerb@student.ethz.ch}.

    \vspace{1\baselineskip}

    Many Thanks
    
    \vspace{1\baselineskip}

    Balázs Szekér
\end{abstract}
\newpage
\thispagestyle{myplain}
\tableofcontents
\pagebreak
\pagenumbering{arabic}
%\setcounter{page}{1}

\section{Complex Functions}

\vspace{1\baselineskip}

\input{1_Complex_Functions/1_Basics.tex}

\vspace{1\baselineskip}

\input{1_Complex_Functions/2_Analytic_Functions.tex}

\vspace{1\baselineskip}

\input{1_Complex_Functions/3_Power_Series.tex}

\vspace{1\baselineskip}

\input{1_Complex_Functions/4_Exponential_and_trigonometric_functions.tex}

\pagebreak

\section{Analytic Functions as Mappings}

\vspace{1\baselineskip}

\input{2_Analytic_Functions_as_Mappings/1_Point_Set_Topology.tex}

\vspace{1\baselineskip}

\input{2_Analytic_Functions_as_Mappings/2_Conformality.tex}

\pagebreak

\section{Complex Integration}

\vspace{1\baselineskip}

\input{3_Complex_Integration/1_Fundamental_Theorems.tex}

\vspace{1\baselineskip}

\input{3_Complex_Integration/2_Cauchys_Integral_Formula.tex}

\vspace{1\baselineskip}

\input{3_Complex_Integration/3_Local_Properties_of_Analytic_Functions.tex}

\vspace{1\baselineskip}

\input{3_Complex_Integration/4_The_General_Form_of_Cauchys_Theorem.tex}

\vspace{1\baselineskip}

\input{3_Complex_Integration/5_The_Calculus_of_Residues.tex}

\pagebreak

\section{Series and Product Developments}

\vspace{1\baselineskip}

\input{4_Series_and_Product_Developments/1_Power_Series_Expansion.tex}

\pagebreak

\input{5_Rest/1_Useful_Tools.tex}

\end{document}