\section{Harvard method}

Fundamendal quesion: "What is the best way for people to deal with each other's
differences?"

Problem: Negotiators tend to bargain over positions and lock themselves into
those positions.

Suggested solution: Focus on principled negotiation or negotiation on the
metris instead of positions (e.g. create respective values)

\subsection{Concept}
Negotiation based on five principles:
\begin{enumerate}
    \item People: Separate the people from the problelem
        \begin{itemize}
            \item Negotiation is interaction between people. Be aware of your
                perception, emotions, and communication.
                \begin{itemize}
                    \item Hard on the facts, soft on the people
                    \item Separate the working relationship from the subject of negotiation
                \end{itemize}
        \end{itemize}
    \item Interests: Focus on interest, not positions
        \begin{itemize}
            \item Many negotiations start based on positions. Identify implicit
                and explicit interests of negotiations behind the positions.
                \begin{itemize}
                    \item Position: manifestation of an interest in a concrete manner.
                    \item Interest: unterlying motivation, concern, and importance
                \end{itemize}
            \item Examples: Window opening, Two sisters want an orange but there
                is only one left (orange peel), 1978 Israeli-Egyptian peace talks after
                6 Day War 1967, Camp David.
        \end{itemize}
    \item Options: Invent options for mutual gain
        \begin{itemize}
            \item Invent and judge options for potential solutions with the aim
                to create mutual gain.
        \end{itemize}
    \item Criteria: Insist on using objective criteria
        \begin{itemize}
            \item Develop, agree upon and apply objective criteria upon which an
                agreement can be derived.
        \end{itemize}
    \item Alternatives: Know your best alternative to a negotiated agreement (BATNA)
        \begin{itemize}
            \item Be aware under which condition an agreement is not in your favor.
        \end{itemize}
\end{enumerate}

\subsection{Criticism}

\begin{itemize}
    \item Not much beyond common sense (professional negotiators are alerady doing this)
    \item It is not scholarly or analytical and relies on anecdotal evidence
    \item It is too simplified for complex situations
    \item "The authors seem to deny the existence of a significant part of the
        negotiation process, and to oversimplify of explain away many of the most
        troublesome problems inherent in the art of practice of negotiation"
\end{itemize}